\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-03-04 manuscript/manuscript.tex
fixed merge conflict

\jy{Sorry I forgot to send you the data I promised. Remind in the future
  please. }

>>>>

Annual temperature minimums were also recorded from Central Park, and the
same method comparison was applied to this series. We found that our method
yields a p-value of 0.0015, Babu's method yields a p-value of 0.2747, and
the parametric method yields a p-value of 0.0002.

\subsection{Temperature in Eastern Asia}
\label{sec:asia}

Annual maximums of daily maximum (TXx) and minimum (TNx) temperatures, and annual 
minimums of daily maximum (TXn) and minimum (TNn) temperatures were collected
for 60 years from 44 locations in Eastern Asia.
\jy{Sorry I forgot to send you the data I promised. Remind in the future
  please. }
